---
title: "Finding Guide"
---

:::{.callout-warning}
# Draft finding guide

<!-- NC will look at getting a good description name into the table. Until we get the categories sorted out under the hood, I'm guessing we can use `exhlabel1` for this purpose and it will not mess up any of the original catalog record.  -->

:::

:::{.callout-tip collapse="true"}
## Expand for tips on using the table

- Use the search box on the right to narrow results.
- Use the dropdown on the left to control the number of records shown. Additional results are paged.
- Page through the table using the controls at the bottom.
- Sort column values by clicking on column labels.
- Filter columns by entering values in the box below colum names.

:::


```{r, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message = FALSE,
                      warning = FALSE)
```

```{r}
library(dplyr)
library(stringr)
library(DT)
```

```{r}
load(file=here::here("tables/df.Rda"))
```

```{r}
df <- df %>% 
  filter(exhibitno == 15) %>% 
  select(objectid, locfield3, locfield4,exhlabel1)
```

```{r}
df$locfield3 <- forcats::fct_drop(df$locfield3)
df$locfield4 <- forcats::fct_drop(df$locfield4)
```

```{r}
df <- df %>%
  mutate(locfield3 = str_replace_all(locfield3, pattern = "^Unit_1$", replacement = "1"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_2$", replacement = "2"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_3$", replacement = "3"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_4$", replacement = "4"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_5$", replacement = "5"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_6$", replacement = "6"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_7$", replacement = "7"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_8$", replacement = "8"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_9$", replacement = "9"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_10$", replacement = "10"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_11$", replacement = "11"),
         locfield3 = str_replace_all(locfield3, pattern = "^Unit_12$", replacement = "12"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_1$", replacement = "1"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_2$", replacement = "2"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_3$", replacement = "3"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_4$", replacement = "4"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_5$", replacement = "5"),
         locfield4 = str_replace_all(locfield4, pattern = "^Shelf_6$", replacement = "6")
  )


```


```{r}
#| column: page

datatable(df, filter = 'top', 
          colnames = c("ID", "Unit", "Shelf", "Label 1"),
          rownames = FALSE,
          options = list(pageLength = 10,
                         autoWidth = TRUE))
```

